---
title: "Business Intelligence Project"
author: "<Specify your name here>"
date: "<Specify the date when you submitted the lab>"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
---

# Student Details

|                                              |     |
|----------------------------------------------|-----|
| **Student ID Number**                        | 127559,134775, 135863, 136346,134141 |
| **Student Name**                             | |
| **BBIT 4.2 Group**                           |c|
| **BI Project Group Name/ID (if applicable)** |Business Intelligent |

# Setup Chunk

```{r}
#installing necessary packages

if(require("caret")){
  require("caret")
}else{
  install.packages("caret", dependencies = TRUE,
                   repos= "https://cloud.r-project.org")
}

if(require("klaR")){
  require("klaR")
}else{
  install.packages("klaR", dependencies = TRUE,
                   repos = "https://cloud.r-prject.org")
}

## e1071 ----
if (require("e1071")) {
  require("e1071")
} else {
  install.packages("e1071", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## readr ----
if (require("readr")) {
  require("readr")
} else {
  install.packages("readr", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## LiblineaR ----
if (require("LiblineaR")) {
  require("LiblineaR")
} else {
  install.packages("LiblineaR", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## naivebayes ----
if (require("naivebayes")) {
  require("naivebayes")
} else {
  install.packages("naivebayes", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}


```


**Note:** the following KnitR options have been set as the global defaults: <BR> `knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE, collapse = FALSE, tidy = TRUE)`.

More KnitR options are documented here <https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and here <https://yihui.org/knitr/options/>.

```{r setup, include=FALSE}
library(formatR)
knitr::opts_chunk$set(
  warning = FALSE,
  collapse = FALSE
)
```

# Understanding the Dataset (Exploratory Data Analysis (EDA))

## Loading the Dataset
```{r}
if (require("mlbench")){
  require("mlbench")
} else {
  install.packages("mlbench", dependencies= TRUE,
                   repos= "https://cloud.r-project.org")
}

#getting/loading the Pima Indians Diabetes dataset from mlbench

data("PimaIndiansDiabetes")
```


### Source:

The dataset that was used can be downloaded here: *\<provide a link\>*

### Reference:

*\<Cite the dataset here using APA\>\
Refer to the APA 7th edition manual for rules on how to cite datasets: <https://apastyle.apa.org/style-grammar-guidelines/references/examples/data-set-references>*

```{r Dataset Loader}
library(readr)

# Provide the executable R code inside the various code chunks as guided by the lab work.
```

#splitting the dataset
```{r}
train_index <- createDataPartition(PimaIndiansDiabetes$diabetes,
                                   p=0.80, list=FALSE)
diabetes_dataset_train <- PimaIndiansDiabetes[train_index,]
diabetes_dataset_test <- PimaIndiansDiabetes[-train_index,]
```

#performing naive bayes
```{r}
diabetes_dataset_nb_e1071 <-
  e1071::naiveBayes(diabetes~ pregnant+ glucose+ pressure+
                      triceps+ insulin+ mass+ pedigree+ age,
                    data=diabetes_dataset_train)
```


#testing the model using the test dataset
```{r}

prediction_nb_e1071 <-
  predict(diabetes_dataset_nb_e1071,
          diabetes_dataset_test[, c("pregnant", "glucose",
                                    "pressure","triceps","insulin", "mass",
                                    "pedigree","age")
            
          ])

print(prediction_nb_e1071)

caret::confusionMatrix(prediction_nb_e1071,
                       diabetes_dataset_test[, c("pregnant", "glucose",
                                                 "pressure","triceps","insulin", "mass",
                                                 "pedigree","age","diabetes")]$diabetes)
```

                                                 
#visualizing the prediction
```{r}
plot(table(prediction_nb_e1071,
           diabetes_dataset_test[, c("pregnant", "glucose",
                                     "pressure","triceps","insulin", "mass",
                                     "pedigree","age","diabetes")]$diabetes))
```

#bootstrapping train control
```{r}
train_control <- trainControl(method = "boot", number = 500)

str(diabetes_dataset_test)


diabetes_dataset_model_lm <- # nolint
  caret::train(diabetes ~
                 pregnant+ glucose+ pressure+
                 triceps+ insulin+ mass+ pedigree+ age,
               data = diabetes_dataset_train,
               trControl = train_control,
               na.action = na.omit, method = "glm", metric = "Accuracy")


predictions_lm <- predict(diabetes_dataset_model_lm,
                          diabetes_dataset_test[, 1:8])
```

##View the RMSE and the predicted values for the 12 observations ----

```{r}
print(diabetes_dataset_model_lm)
print(predictions_lm)

```
#perfoming 10 fold cross validation
```{r}

train_control <- trainControl(method = "cv", number = 10)

diabetes_dateset_model_lm_cv <-
  caret::train(diabetes ~ .,
               data = diabetes_dataset_train,
               trControl = train_control, na.action = na.omit,
               method = "glm", metric = "Accuracy")


predictions_lm_cv <- predict(diabetes_dateset_model_lm_cv, diabetes_dataset_test[, -9])


print(diabetes_dateset_model_lm_cv)
print(predictions_lm_cv)

```
#performing Classification: SVM with Repeated k-fold Cross Validation
```{r}

train_control <- trainControl(method = "repeatedcv", number = 5, repeats = 3)


diabetes_dateset_model_svm <-
  caret::train(diabetes ~ ., data = diabetes_dataset_train,
               trControl = train_control, na.action = na.omit,
               method = "svmLinearWeights2", metric = "Accuracy")

predictions_svm <- predict(diabetes_dateset_model_svm, diabetes_dataset_test)


print(diabetes_dateset_model_svm)
caret::confusionMatrix(predictions_svm, diabetes_dataset_test$diabetes)


```
#training a Naive Bayes classifier based on an LOOCV

```{r}
train_control <- trainControl(method = "LOOCV")


diabetes_dataset_model_nb_loocv <-
  caret::train(diabetes ~ ., data = diabetes_dataset_train,
               trControl = train_control, na.action = na.omit,
               method = "naive_bayes", metric = "Accuracy")

predictions_nb_loocv <-
  predict(diabetes_dataset_model_nb_loocv, diabetes_dataset_test[, 1:9])

print(diabetes_dataset_model_nb_loocv)
caret::confusionMatrix(predictions_nb_loocv, diabetes_dataset_test$diabetes)

```

